---
title: "Data Analysis - Final Project-Sena"
author: "SenaKaya"
date: "2023-06-09"
output: html_document
---

```{r setup, include=FALSE}
```

#read the dataset
#first 5 row

```{r }
library(readxl)
heartd<- read.csv("/Users/senakaya/Desktop/UCSC/data analysis/final-Personal Key Indicators of Heart Disease/heart_2020_cleaned.csv")
head(heartd)
```

#dimension of dataset

```{r }
dim(heartd)
```
#to checks number of null values
```{r}
sum(heartd.stringsAsFactors=FALSE)
sum(is.na(heartd))
```
#a list of objects and their structure
```{r}
str(heartd)
```

#summary of the dataset
```{r}
summary(heartd)
```
#table of HeartDisease
```{r}
table(heartd$HeartDisease)
```

#the number of different values for each column
```{r}
library(dplyr)
heartd %>% summarise_all(n_distinct)
```
#EDA (EXPLORATORY DATA ANALYSIS)
#histogram of BMI(Body Mass Index)
```{r}
library(ggplot2)

p<-ggplot(data = heartd, aes(x = BMI)) + geom_histogram(binwidth = 3,fill='blue',colour="red")+ coord_cartesian(xlim = c(10, 60))
p+ geom_vline(aes(xintercept=mean(BMI)), color="yellow", linetype="dashed", linewidth=1)
```

#histogram of Physical Health
```{r}
p<-ggplot(data = heartd, aes(x = heartd$PhysicalHealth)) + geom_histogram(binwidth = 3,fill='blue',colour="red")+ coord_cartesian(xlim = c(0, 30))
p+ geom_vline(aes(xintercept=mean(heartd$PhysicalHealth)), color="yellow", linetype="dashed", size=1)
```

#histogram of Mental Health
```{r}
p<-ggplot(data = heartd, aes(x = MentalHealth )) + geom_histogram(binwidth = 3,fill='blue',colour="red")+ coord_cartesian(xlim = c(0, 30))
p+ geom_vline(aes(xintercept=mean(MentalHealth)), color="yellow", linetype="dashed", size=1)
```

#histogram of Sleep Time
```{r}
p<-ggplot(data = heartd, aes(x = SleepTime)) + geom_histogram(binwidth = 1,fill='blue',colour="red")+ coord_cartesian(xlim = c(2, 12))
p+ geom_vline(aes(xintercept=mean(SleepTime)), color="yellow", linetype="dashed", size=1)
```

#remove the scientific notations from the axis
```{r}
options(scipen = 999)
```

#Create the stacked bar plot for two categorical variable heart disease and smoking
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = Smoking)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))
  ggtitle("Bar Plot of Heart Disease and Smoking")
```

#Create the stacked bar plot for two categorical variable heart disease and alcohol drinking
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = AlcoholDrinking)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))+
  ggtitle("Bar Plot of Heart Disease and Alcohol Drinking")
```

#Create the bar stacked plot for two categorical variable heart disease and sex
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = Sex)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))+
  ggtitle("Bar Plot of Heart Disease and Sex")
```

#Create the stacked bar plot for two categorical variable heart disease and asthma
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = Asthma)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))+
  ggtitle("Bar Plot of Heart Disease and Asthma")
```

#Create the stacked bar plot for two categorical variable heart disease and kidney disease
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = KidneyDisease)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))+
  ggtitle("Bar Plot of Heart Disease and Kidney Disease")
```

#Create the stacked bar plot for two categorical variable heart disease and skin cancer
```{r}
ggplot(heartd, aes(x = HeartDisease, fill = SkinCancer)) +
  geom_bar() +
  xlab("HeartDisease") +
  ylab("Count") +
  coord_cartesian(ylim = c(0, 300000))+
  ggtitle("Bar Plot of Heart Disease and Skin Cancer")
```

#Count the frequencies of each combination of the two variables
#Create the bar chart
```{r}
counts <- table(heartd$HeartDisease, heartd$Smoking)

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count",
        main = "Bar Chart of Heart Disease and Smoking")
```

#Count the frequencies of each combination of the two variables
#Define colors for the bars
#Create the bar chart
```{r}
counts <- table(heartd$HeartDisease, heartd$AgeCategory)

colors <- c("yellow", "green")  

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count",
        main = "Bar Chart of Heart Disease and Age Category", col = colors)
```

#Count the frequencies of each combination of the two variables

```{r}
counts <- table(heartd$HeartDisease, heartd$Race)

colors <- c("yellow", "green")  

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count",
        main = "Bar Chart of HeartDisease and Race", col = colors)
```

#Count the frequencies of each combination of the two variables

```{r}
counts <- table(heartd$HeartDisease, heartd$GenHealth)

colors <- c("yellow", "green")  

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count",
        main = "Bar Chart of HeartDisease and GenHealth", col = colors)
```

# Count the frequencies of each combination of the two variables

```{r}
counts <- table(heartd$HeartDisease, heartd$SleepTime)

colors <- c("yellow", "green")  

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count", 
        main = "Bar Chart of HeartDisease and Sleep Time", col = colors)
```

# Count the frequencies of each combination of the two variables

```{r}
counts <- table(heartd$HeartDisease, heartd$PhysicalHealth)

colors <- c("yellow", "green")  

barplot(counts, beside = TRUE, legend = TRUE,
        xlab = "HeartDisease", ylab = "Count", 
        main = "Bar Chart of HeartDisease and Physical Health", col = colors)
```

# Replace values in the data frame
```{r}
heartd <- replace(heartd, heartd == 'Yes', 1)
heartd <- replace(heartd, heartd == 'No', 0)
heartd <- replace(heartd, heartd == 'Male', 1)
heartd <- replace(heartd, heartd == 'Female', 0)
heartd <- replace(heartd, heartd == 'No, borderline diabetes', 0)
heartd <- replace(heartd, heartd == 'Yes (during pregnancy)', 1)
#ordinal
heartd <- replace(heartd, heartd == 'Excellent', 5)
heartd <- replace(heartd, heartd == 'Very good', 4)
heartd <- replace(heartd, heartd == 'Good', 3)
heartd <- replace(heartd, heartd == 'Fair', 2)
heartd <- replace(heartd, heartd == 'Poor', 1)
```

# Convert 'Diabetic' column to integer
```{r}
heartd$Diabetic <- as.numeric(heartd$Diabetic)
```

# Extract the first two characters from the "Age" column
```{r}
heartd$AgeCategory <- substr(heartd$AgeCategory, 1, 2)
```

# Print the first five row of modified "Age" column
```{r}
print(heartd$AgeCategory[1:5])
```

#convert all "0"s and "1"s to integer except c( "Race")
```{r}
num_columns <- setdiff(colnames(heartd), c( "Race"))

heartd_num <- as.data.frame(lapply(heartd[num_columns], as.numeric))

str(heartd_num)
```
```{r}
library(reshape2)
library(RColorBrewer)
library(corrplot)

library(ggcorrplot)
```

#Create correlation matrix
#Plot correlation matrix
#Calculate the correlation matrix
```{r}
cor_matrix <- cor(heartd_num)

ggcorrplot(cor_matrix, type = "lower") +
  geom_tile() +
  scale_fill_gradientn(colours = brewer.pal(11, "RdBu"),
                       limits = c(-1, 1),
                       breaks = seq(-1, 1, by = 0.2)) +
  
  labs(x = "", y = "") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


cor_matrix <- cor(heartd_num)

print(cor_matrix)
```


#Find correlations above 0.75
#Check if there are any high correlations
```{r}
high_corr <- which(cor_matrix > 0.75 & cor_matrix < 1, arr.ind = TRUE)

if (nrow(high_corr) == 0) {
  cat("No correlations above 0.75 found.\n")
} else {
  # Print the pairs of variables with high correlation
  for (i in 1:nrow(high_corr)) {
    row_num <- high_corr[i, "row"]
    col_num <- high_corr[i, "col"]
    row_name <- rownames(cor_matrix)[row_num]
    col_name <- colnames(cor_matrix)[col_num]
    correlation <- cor_matrix[row_num, col_num]
    cat("High correlation (", correlation, ") between", row_name, "and", col_name, "\n")
  }
}

```

#Create a copy of the original data frame
```{r}
df_encoded <- heartd
str(df_encoded)
```


#ONE-HOT ENCODING
#Perform one-hot encoding for the "Race" column
```{r}
df_encoded <- heartd
```

#Extract the "Race" column
```{r}
race_column <- df_encoded$Race
```

#Perform one-hot encoding for the "Race" column
```{r}
encoded_cols <- model.matrix(~ 0 + factor(race_column))
colnames(encoded_cols) <- paste("Race", colnames(encoded_cols), sep = "_")
```

#Add the encoded columns to the data set
```{r}
df_encoded <- cbind(df_encoded, encoded_cols)
```

#Remove the original "Race" column
```{r}
df_encoded <- df_encoded[, !names(df_encoded) %in% "Race"]
```

#Print the encoded data set
```{r}
print(head(df_encoded))
str(df_encoded)
```

#Convert specific columns to integers (only independent variables - dependent variable must be a factor)
```{r}
columns_to_convert <- c("Smoking", "SkinCancer", "KidneyDisease", "Asthma", "GenHealth", 
                        "AgeCategory","Stroke", "AlcoholDrinking","Sex", "DiffWalking", "PhysicalActivity")
df_encoded[columns_to_convert] <- lapply(df_encoded[columns_to_convert], as.numeric)
```

#Identify numeric variables in the data frame
```{r}
numeric_vars <- sapply(df_encoded, is.numeric)

str(df_encoded)
```

SCALING
#Apply min-max scaling to the numerical variables
```{r}
scaled_data <- apply(df_encoded[, numeric_vars], 2, function(x) (x - min(x)) / (max(x) - min(x)))
```

#Print the scaled data
```{r}
print(head(scaled_data))
```

#Combine the scaled numeric variables with the non-numeric variables
```{r}
scaled_dataframe <- cbind(scaled_data, df_encoded[!numeric_vars])
str(scaled_dataframe)
```

#Print the scaled data frame
```{r}
print(head(scaled_dataframe))
max(scaled_dataframe$BMI)
min(scaled_dataframe$BMI)
```

```{r}
# install.packages("caret", dependencies = c("Depends", "Suggests"))
```

```{r}
#install.packages('gower')
```
```{r}
# install.packages('hardhat')
```

```{r}
# install.packages('timechange')
```

```{r}
# install.packages('ModelMetrics')
```
```{r}
library(ggplot2)
library(lattice)
library(caret)
```
#SPLITING TEST AND TRAIN DATA SET

#Set the random seed for reproducibility
#Specify the proportion of data to be allocated for the test set
#Create the train and test split
```{r}
set.seed(123)

test_size <- 0.2

split <- createDataPartition(scaled_dataframe$HeartDisease, p = test_size, list = FALSE)
```

#Create the train set
#Create the test set
```{r}
 test_set<- scaled_dataframe[split, ]

 train_set <- scaled_dataframe[-split, ]
```

#dimension of test and train set
```{r}
dim(test_set)
dim(train_set)
```

MODELLING
Logistic Regression

#Create the formula for logistic regression
```{r}
formula <- as.formula( HeartDisease ~ .)
```

#Convert the "HeartDisease" column to factor in both train_set and test_set
```{r}
train_set$HeartDisease <- factor(train_set$HeartDisease)
test_set$HeartDisease <- factor(test_set$HeartDisease)
```

#Train the logistic regression model
```{r}
weight = 0.8
model <- glm(formula, data = train_set, 
             family = "binomial",
             weights = ifelse(train_set$HeartDisease == 1, weight, 1 - weight)
             )

```

#Make predictions on the test set
```{r}
predictions <- predict(model, newdata = test_set, type = "response")
```

#Convert the predictions to binary values
```{r}
binary_predictions <- ifelse(predictions > 0.5, 1, 0)
```

#Calculate accuracy
```{r}
accuracy <- mean(binary_predictions == test_set$HeartDisease)
cat("Accuracy:", accuracy, "\n")

TP <- sum(binary_predictions == 1 & test_set$HeartDisease == 1)
FN <- sum(binary_predictions == 0 & test_set$HeartDisease == 1)
```

#recall <- sensitivity(as.factor(test_set$HeartDisease), as.factor(predictions))
```{r}
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")
```

#Calculate precision
```{r}
precision <- sum(binary_predictions == 1 & test_set$HeartDisease == 1) / sum(binary_predictions == 1)
cat("Precision:", precision, "\n")
```

#Calculate F1 score
```{r}
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#Confusion Matrix
```{r}
confusionMatrix(data=as.factor(binary_predictions), reference = as.factor(test_set$HeartDisease))
```

KNN Classifier

#Train the KNN classifier
```{r}
library(caret)
k <- 5
formula <- as.formula(HeartDisease ~ .)
model <- train(formula, data = train_set, method = "knn", trControl = trainControl(method = "none"), tuneGrid = data.frame(k = k))
```

#Make predictions on the test an training set
```{r}
predictions <- predict(model, newdata = test_set)
predictions_train <- predict(model, newdata = train_set)
```

#Calculate accuracy
```{r}
accuracy <- sum(predictions == test_set$HeartDisease) / length(test_set$HeartDisease)
cat("Accuracy:", accuracy, "\n")
accuracy_train <- sum(predictions_train == train_set$HeartDisease) / length(train_set$HeartDisease)
cat("Accuracy_Train:", accuracy_train, "\n")
```

#Calculate true positives
```{r}
true_positives <- sum(predictions == 1 & test_set$HeartDisease == 1)
print(true_positives)
```

#Calculate false positives
```{r}
false_positives <- sum(predictions == 1 & test_set$HeartDisease == 0)
print(false_positives)
```

#Calculate false negatives
```{r}
false_negatives <- sum(predictions == 0 & test_set$HeartDisease == 1)
print(false_negatives)
```

#Calculate recall
```{r}
recall <- true_positives / (true_positives + false_negatives)
cat("Recall:", recall, "\n")
```

#Calculate precision
```{r}
precision <- true_positives / (true_positives + false_positives)
cat("Precision:", precision, "\n")
```

#Calculate F1 score
```{r}
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#Confusion Matrix of the test set
```{r}
confusionMatrix(data=as.factor(predictions), reference = as.factor(test_set$HeartDisease))
```

#Confusion Matrix of the train set
```{r}
confusionMatrix(data=as.factor(predictions_train), reference = as.factor(train_set$HeartDisease))
```

#RANDOM FOREST
```{r}
library(randomForest)
```

#Get the current column names
```{r}
column_names <- names(train_set)
column_names_test <- names(test_set)
```

#Replace "/" and " " with "_"
```{r}
new_column_names <- gsub("/", "_", column_names)
new_column_names_test <- gsub("/", "_", column_names_test)

new_column_names <- gsub(" ", "_", new_column_names)
new_column_names_test <- gsub(" ", "_", new_column_names_test)
```

#Rename columns with similar issues
```{r}
new_column_names <- sub(".*\\)", "Race_", new_column_names)
new_column_names_test <- sub(".*\\)", "Race_", new_column_names_test)
```

#Assign the new column names to the dataset
```{r}
names(train_set) <- new_column_names
names(test_set) <- new_column_names_test

```

```{r}
library(dplyr)
```

#Define the parameter grid for tuning
```{r}
ntree_vals <- c(25,30,35,40,45,50,100)
mtry_vals <- c(sqrt(ncol(train_set)))
nodesize_vals <- c(20)
```

#Initialize empty dataframe to store results
```{r}
results <- data.frame(ntree = integer(),
                      mtry = numeric(),
                      nodesize = integer(),
                      class_weight = character(),
                      accuracy = numeric(),
                      recall = numeric(),
                      precision = numeric(),
                      f1_score = numeric(),
                      stringsAsFactors = FALSE)
```

#Define the best metric value and class weights
```{r}
best_metric <- 0
best_class_weights <- NULL
best_ntree <- 0
best_mtry <- 0
best_nodesize <- 0
```

#Iterate over parameter combinations
```{r}
for (ntree in ntree_vals) {
  for (mtry in mtry_vals) {
    for (nodesize in nodesize_vals) {
      # Iterate over class weight combinations
      for (weight_1 in seq(0.3, 0.6, 0.4)) {
        weight_0 <- 1 - weight_1
        class_weights <- list(weight_0, weight_1)

        # Train the Random Forest model with current parameter combination and class weight
        model <- randomForest(HeartDisease ~ ., 
                              data = train_set, 
                              ntree = ntree,
                              mtry = mtry,
                              importance = TRUE,
                              nodesize = nodesize,
                              classwt = class_weights)
        
        # Make predictions on the test set
        predictions <- predict(model, newdata = test_set)
        
        # Calculate metrics
        TP <- sum(predictions == 1 & test_set$HeartDisease == 1)
        FN <- sum(predictions == 0 & test_set$HeartDisease == 1)
        
        accuracy <- mean(predictions == test_set$HeartDisease)
        recall <- TP / (TP + FN)
        precision <- sum(predictions == 1 & test_set$HeartDisease == 1) / sum(predictions == 1)
        f1_score <- 2 * (precision * recall) / (precision + recall)
        
        # Append results to dataframe
        results <- results %>% 
          add_row(ntree = ntree,
                  mtry = mtry,
                  nodesize = nodesize,
                  class_weight = paste(class_weights, collapse = ":"),
                  accuracy = accuracy,
                  recall = recall,
                  precision = precision,
                  f1_score = f1_score)
        # Check if the current class weight combination improves the best metric
        if (f1_score > best_metric) {
          best_metric <- f1_score
          best_class_weights <- class_weights
          best_ntree <- ntree
          best_mtry <- mtry
          best_nodesize <- nodesize
        }
      }
    }
  }
}
```

#View the results
```{r}
print(results)
cat('\n')
```

#Print the best class weights and metric value
```{r}
cat("Best Class Weights:", paste(best_class_weights, collapse = ":"), "\n")
cat("best_ntree:", best_ntree, "\n")
cat("best_mtry:", best_mtry, "\n")
cat("best_nodesize:", best_nodesize, "\n")
cat("Best F1 Score:", best_metric, "\n")
```

#BEST RANDOM FOREST MODEL
```{r}
model <- randomForest(HeartDisease ~ ., 
                      data = train_set, 
                      ntree = best_ntree,           # Number of trees in the forest
                      mtry = best_mtry,             # Number of variables to consider at each split
                      importance = TRUE,            # Calculate variable importance
                      nodesize = best_nodesize,     # Minimum size of terminal nodes
                      classwt = best_class_weights  # Assign class weights
)
```

#Make predictions on the test set
```{r}
predictions <- predict(model, newdata = test_set)
predictions_train <- predict(model, newdata = train_set)
```

#Calculate accuracy
```{r}
accuracy <- mean(predictions == test_set$HeartDisease)
cat("Accuracy for test_set:", accuracy, "\n")

accuracy_train <- mean(predictions_train == train_set$HeartDisease)
cat("Accuracy Training:", accuracy_train, "\n")
```

#Recall
```{r}
TP <- sum(predictions == 1 & test_set$HeartDisease == 1)
FN <- sum(predictions == 0 & test_set$HeartDisease == 1)
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")

TP <- sum(predictions_train == 1 & train_set$HeartDisease == 1)
FN <- sum(predictions_train == 0 & train_set$HeartDisease == 1)
recall_train <- TP / (TP + FN)
cat("Recall_Train:", recall_train, "\n")
```

#Calculate precision
```{r}
precision <- sum(predictions == 1 & test_set$HeartDisease == 1) / sum(predictions == 1)
cat("Precision:", precision, "\n")

precision_train <- sum(predictions_train == 1 & train_set$HeartDisease == 1) / sum(predictions_train == 1)
cat("Precision_train:", precision_train, "\n")
```

#Calculate F1 score
```{r}
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")

f1_score_train <- 2 * (precision_train * recall_train) / (precision_train + recall_train)
cat("F1 Score Train:", f1_score_train, "\n")
```

#Confusion matrix for test set
```{r}
confusionMatrix(data=as.factor(predictions), reference = as.factor(test_set$HeartDisease))
```

#Confusion Matrix for train set
```{r}
confusionMatrix(data=as.factor(predictions_train), reference = as.factor(train_set$HeartDisease))
```

#Feature Importances
```{r}
library(caret)
library(ggplot2)
```

#Calculate feature importances
```{r}
importances <- varImp(model)
```

#Sort the importances in descending order
```{r}
sorted_importances <- importances[order(importances$`0`, decreasing = TRUE), ]
sorted_importances = subset(sorted_importances, select = -c(1) )
```

#Print feature importances
```{r}
print(sorted_importances)
```

#Create a dataframe for plotting
```{r}
importance_df <- data.frame(variable = row.names(sorted_importances),
                            importance = sorted_importances)
```

#Plot the feature importances in a horizontal bar chart
```{r}
ggplot(importance_df, aes(y = reorder(variable, X1), x = X1)) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label = round(X1,1)), hjust = -0.1, size = 3, color = "black") +
  labs(y = "Variable", x = "Importance") +
  ggtitle("Feature Importances") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
library(caret)
```

#Define the range of weights to be tested
```{r}
weight_range <- seq(0.1, 1, by = 0.1)
```

#Initialize an empty dataframe to store results
```{r}
results_LR <- data.frame(weights = character(),
                         accuracy = numeric(),
                         recall = numeric(),
                         precision = numeric(),
                         f1_score = numeric(),
                         stringsAsFactors = FALSE)
```

#Perform parameter tuning with different class weights
```{r}
model <- glm(HeartDisease ~ ., 
             data = train_set, 
             family = "binomial")
class_weights <- 'Default'

for (weight in weight_range) {
  # Train the logistic regression model with class weights
  
  
  # Make predictions on the test set
  predictions <- predict(model, newdata = test_set, type = "response")
  
  # Convert predictions to factors
  predictions <- as.factor(ifelse(predictions > 0.5, 1, 0))
  
  # Calculate evaluation metrics
  TP <- sum(predictions == 1 & test_set$HeartDisease == 1)
  FN <- sum(predictions == 0 & test_set$HeartDisease == 1)
  
  accuracy <- mean(predictions == test_set$HeartDisease)
  #recall <- sensitivity(as.factor(test_set$HeartDisease), as.factor(predictions))
  recall <- TP / (TP + FN)
  precision <- sum(predictions == 1 & test_set$HeartDisease == 1) / sum(predictions == 1)
  f1_score <- 2 * (precision * recall) / (precision + recall)
  
  # Append results to the dataframe
  
  results_LR <- rbind(results_LR, data.frame(weights = class_weights,
                                             accuracy = accuracy,
                                             recall = recall,
                                             precision = precision,
                                             f1_score = f1_score,
                                             stringsAsFactors = FALSE))

  class_weights <- paste(1 - weight, weight, sep = ":")
  model <- glm(HeartDisease ~ ., 
               data = train_set, 
               family = "binomial",
               weights = ifelse(train_set$HeartDisease == 1, weight, 1 - weight))
}

# Print the results
print(results_LR)
```















